Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-17 appendix.qmd
Reorganized video link table

# Create the table
kable(notation_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("3cm", "12cm"))
```

>>>>

# Create the table
kable(notation_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("3cm", "12cm"))
```

### 2025-06-17 paper.qmd
Reorganized video link table

The R package `quollr`, available on CRAN and at [https://jayanilakshika.github.io/quollr/](https://jayanilakshika.github.io/quollr/), provides software accompaying this paper to fit the wireframe model representation, compute diagnostics, visualize the model in the data with langevitour and link multiple plots interactively.

Direct links to videos for viewing online are available in @tbl-links.

@@

# Create the table
kable(links_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("1.5cm", "4.5cm"))
```

>>>>

The R package `quollr`, available on CRAN and at [https://jayanilakshika.github.io/quollr/](https://jayanilakshika.github.io/quollr/), provides software accompaying this paper to fit the wireframe model representation, compute diagnostics, visualize the model in the data with langevitour and link multiple plots interactively. Direct links to videos for viewing online are available in @tbl-links.

@@

# Create the table
kable(links_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("1.5cm", "14cm"))
```
